---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# compassutils

<!-- badges: start -->
<!-- badges: end -->

The goal of compassutils is to supply useful plotting and/or utility functions for working with output from COMPASS. 

## Installation

You can install the latest version of computils from [GitHub](https://www.github.com) with 

```{r , eval = FALSE}
if(!require("devtools", quietly = TRUE)) install.packages('devtools')
devtools::install_github("SATVILab/compassutils.git")
```

## Example

You can create a box- and dot-plot(s) of posterior probabilities for individual cytokine combinations (more concise than `COMPASS::plot` heatmap):

```{r example, eval = FALSE}
library(compassutils)
data('c_obj', package = compassutils)
plot_compass(c_obj = c_obj)
```

You can convert cytokine combination formats between standard "+/-" format and COMPASS "!&" format. 
```{r , eval = FALSE}
library(compassutils)
data('c_obj', package = compassutils)
plot_compass(c_obj = c_obj)
```

