---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# compassutils

<!-- badges: start -->
<!-- badges: end -->

The goal of compassutils is to supply useful plotting and utility functions for working with output from COMPASS. 

## Installation

You can install the latest version of computils from [GitHub](https://www.github.com) with 

```{r , eval = FALSE}
if(!require("devtools", quietly = TRUE)) install.packages('devtools')
devtools::install_github("SATVILab/compassutils.git")
```

## Example

### Plots

You can create a box- and dot-plot(s) of posterior probabilities for individual cytokine combinations. These are more concise than standard `COMPASS` heatmaps and automatically force the same cytokine combinations to be present and cytokines in the same order for all "groups" plotted together. 

```{r example-plot_compass}
library(compassutils)
data('c_obj_list', package = 'compassutils')
plot_compass(c_obj = c_obj_list[c(1,3)], save = FALSE, 
             shift_plot_grid = 0.063)
```

### Utilities

You can convert cytokine combination formats between standard "+/-" format and COMPASS "!&" format. 
```{r , results = 'asis'}
cyt_combn_vec_compass <- c("IFNg&!IL2&TNF&IL6&!IL22",
                           "IFNg&IL2&TNF&IL6&IL22",
                           "!IFNg&!IL2&!TNF&!IL6&!IL22")
cyt_combn_vec_std <- compassutils::convert_cyt_combn_format(cyt_combn_vec_compass, 
                                                            to = 'std')
pander::pandoc.table(tibble::tibble(
  `COMPASS format` = cyt_combn_vec_compass, 
  `Standard format` = cyt_combn_vec_std 
  ))
```

